Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-01-26 msr/msr2011.tex
Tiny edits

This paper makes the following contributions: 
\begin{itemize}
\item introduces the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels; 
\item evaluates an unsupervised method of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
\item evaluates a supervised method of automatically labelling topics with a single NFR (machine learning);
\item evaluates a supervised method of labelling topics with multiple NFRs (multi-label machine learning);
\item provides a method of cross-project analysis via topic labelling; and
\item applies these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}

@@

\begin{figure*}[]
\centering
\subfloat[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline}
\label{fig:mysql-timeline}                               
}

>>>>

This paper makes the following contributions: 
\begin{itemize}
\item we introduce the concept of labelled topic extraction, using a non-functional requirements (NFR) taxonomy for our labels; 
\item we evaluate an unsupervised method of automated topic labelling (word-lists);
%\item Our unsupervised method can be applied to projects without training;
\item we evaluate a supervised method of automatically labelling topics with a single NFR (machine learning);
\item we evaluate a supervised method of labelling topics with multiple NFRs (multi-label machine learning);
\item we provide a method of cross-project analysis via topic labelling; and
\item we apply these techniques to visualize NFRs over time, and to analyze maintenance activities.
\end{itemize}

@@

\begin{figure*}[t]
\centering
\subfloat[MySQL 3.23]{
\includegraphics[width=\textwidth]{figures/mysql-timeline}
\label{fig:mysql-timeline}                               
}
